\chapter{Understanding QoE Problems in the Wild}
\label{ch:measurement}

The key role that QoE plays in impacting user engagement,
and consequently providers' revenues, has motivated recent
efforts, including this dissertation, in improving the QoE of 
Internet applications like
Internet video and Internet telephony.
Before we embark on designing and deploying new 
schemes to improve QoE, we need to first understand 
the nature of QoE problems.
To this end, this section uses large-scale datasets collected
from real users to shed light on the structure of today's 
QoE problems  in the wild.
In particular, we observe that 
(1) a substantial fraction of video and VoIP 
sessions suffer from QoE problems; and
(2) QoE problems exhibit patterns both 
spatially (e.g., correlation to
certain client-side features) and temporally
(e.g., prevalent/persistent quality issues).

This chapter is organized as follows.
Section~\ref{sec:measurement:video} presents a 
measurement study on video QoE.
Using 300 million video sessions collected over a 
two-week period, we show how severe today's
QoE problems are, and  analyze the spatial
and temporal properties of these QoE problems.
Section~\ref{sec:measurement:voip} presents
a similar measurement study on Internet telephony 
QoE based on a dataset from one of the most 
popular VoIP  service providers.
Finally, Section~\ref{sec:measurement:summary} 
summarizes the chapter with key findings 
which motivate the ideas proposed in later 
chapters.

\input{patterns-video}

\input{patterns-voip}





\section{Summary}
\label{sec:measurement:summary}

In this chapter, we have used large-scale measurement
from real users to quantify quantify quality problems of
Internet video and Internet telephony in the wild.
Our findings can be summarized as follows:

\begin{itemize}

\item {\em Quality today is not idea.} 
Across multiple application providers, we observe 
that a substantial fraction of sessions have bad quality. 
For instance, 5\% video sessions have a
buffering ratio larger than 10\%, and 15-17\% Skype
calls have bad network performance in at least one
of long latency, high packet loss, or high latency jitter.

\item {\em Most quality problems can be attributed to 
a relatively small amount of persistent patterns.}
We observe that in both Internet video and Internet
telephony, bad quality can be attributed to some
session-level features (e.g., critical clusters in 
Section~\ref{subsec:measurement:video:temporal}
and AS pairs in 
Section~\ref{subsec:measurement:voip:temporal}).
These quality problems and features are more stable than 
fluctuation of quality.

\item {\em Metrics are correlated.} Finally, we observed that
quality problems of different metrics are likely to be correlated
suggesting that it is possible to improve multiple metrics 
simultaneously.

\end{itemize}





