\chapter{Predictive QoE Optimization By Critical Feature Analysis}
\label{ch:cfa}

\newcommand{\dda}{{CFA}\xspace}
\newcommand{\system}{{\dda}\xspace}
\newcommand{\ControlPlane}{{global optimization system}\xspace}

In this chapter, we present the first illustration of how \ddn paradigm 
improves video QoE by formulating \ddn as a prediction problem. The goal is 
to predict video quality  for different choices (e.g., CDN 
or bitrate) to make optimal decisions.
As many prior efforts have suggested, such  {\em data-driven prediction} of 
video quality can potentially lead to substantial video QoE improvement.
%Many prior efforts have suggested that Internet video 
%QoE  could be dramatically improved by using {\em data-driven 
%prediction} of video quality  for different choices (e.g., CDN 
%or bitrate) to make optimal decisions.
However, building such a prediction system is challenging on two fronts. 
First, the relationships between video quality and observed 
session features can be quite complex. Second, video quality changes 
dynamically. 
Thus, we need a prediction model that is 
(a) expressive enough to capture these complex relationships, 
and (b) capable of updating quality predictions in near 
real-time. 
Unfortunately, several seemingly natural solutions (e.g., 
simple machine learning approaches and simple network models) fail on 
one or more fronts.
%Thus, the potential benefits promised by these prior
%efforts remain unrealized. 

To address these challenges, we present {\em Critical 
Feature Analytics (\dda)}, which is inspired by  persistent
structures in QoE-determining factors. 
In particular, video quality is typically determined by a small subset of 
critical features whose criticality persists over several tens of minutes.
This enables a scalable and accurate workflow where 
we automatically learn critical features for different 
sessions on coarse-grained timescales, while updating 
quality predictions in  near real-time. 
Using a  combination of a real-world pilot deployment 
and trace-driven analysis, we demonstrate that \dda 
leads to significant improvements in video quality; e.g., 32\% less 
buffering time and 12\% higher bitrate than a random decision maker.

This chapter is organized as follows.
Section~\ref{sec:cfa:background} provides some background on
the promise of video QoE prediction, and identifies key challenges
 in building an accurate video QoE prediction
system.
Then Section~\ref{sec:cfa:outline}, Section~\ref{sec:cfa:design},
and Section~\ref{sec:cfa:impl} outlines the key design ideas 
behind CFA, the detailed design, and implementation of CFA, respectively.
Section~\ref{sec:cfa:eval} presents real-world and trace-driven evaluation that 
demonstrates substantial quality improvement by CFA.
Section~\ref{sec:cfa:insight} uses critical features learned by 
CFA to make interesting
observations about video quality.
Finally, Section~\ref{sec:cfa:discuss} discusses some open issues in 
CFA, Section~\ref{sec:cfa:related} discusses the related work, and 
Section~\ref{sec:cfa:summary} concludes the section.


\input{cfa-background}

\input{cfa-outline}

\input{cfa-design}

\input{cfa-impl}

\input{cfa-eval}

\input{cfa-discuss}

\input{cfa-related}

\section{Summary}
\label{sec:cfa:summary}

This chapter presents the first illustration of how \ddn can be used
to improves video QoE. 
In particular, we have formulated data-driven
QoE optimization as  a prediction problem, which as shown by prior
research efforts could lead to improved QoE. 
However, prior efforts have failed to provide a prescriptive solution
that (a) is expressive enough to tackle the complex
feature-quality relationships observed in the wild and (b)
can provide near real-time quality estimates. To this end,
we developed CFA, a solution based on domain-specific
insight of persistent structures (critical features) 
that video quality is typically determined by a
subset of critical features which tend to be persistent.
CFA leverages these insights to engineer an accurate algorithm
that outperforms off-the-shelf machine learning
approaches and lends itself to a scalable implementation
that retains model freshness. Using real deployments and
trace-driven analyses, we showed that CFA achieves up
to 30\% improvement in prediction accuracy and 12-32\%
improvement in QoE over alternative approaches.
%
%Many prior research efforts posited that quality prediction
%could lead to improved QoE.
%However, these efforts failed to provide a prescriptive solution
%that (a) is expressive enough to tackle the complex
%feature-quality relationships observed in the wild and (b)
%can provide near real-time quality estimates. To this end,
%we developed CFA, a solution based on domain-specific
%insights that video quality is typically determined by a
%subset of critical features which tend to be persistent.
CFA leverages these insights to engineer an accurate algorithm
that outperforms off-the-shelf machine learning
approaches and lends itself to a scalable implementation
that retains model freshness. Using real deployments and
trace-driven analyses, we showed that CFA achieves up
to 30\% improvement in prediction accuracy and 12-32\%
improvement in QoE over alternative approaches.




